\section{Concluding remarks\label{section:CR}}
\noindent
This paper has analyzed the coordination problem that arises between a mothership vehicle and a fleet of drones that must coordinate their routes to minimize the total time traveled by the mothership while visiting a set of targets modeled by graphs. We have presented exact mixed integer nonlinear programming formulations of the problem for its complete and partial overlapping versions. Moreover, we strengthen the models with some valid inequalities for them. }\\
Our computational results show that the considered problem is very challenging to solve even on small and medium size instances. For that reason, additionally, we have proposed a matheuristic algorithm that provides good quality feasible solutions in a short computing time; so that it is a good alternative to the exact method. We report extensive computational experiments on randomly generated instances. Moreover, we present a case study related to inspection activities in the context of COVID-19 restrictions. We show the application of the system described in this paper in the framework of the Courtyard Festival in the city of Cordoba, by illustrating the solution obtained by adopting the problem formulation, in both versions of the model, and its solution by means of the initialization provided by the proposed matheuristic.\\
\noindent
The formulation and algorithms proposed in this paper can be seen \JP{as} a first building block to handle the coordination of systems \JP{composed by a base vehicle and a number of  drones.} Further research in this topic must focus on finding faster and more accurate algorithms able to solve larger size instances. Moreover, it is also challenging to model more complex operations allowing that drones can visit more than one target per trip. Other extensions that may be considered can take into account that the time spent by the mothership to launch and retrieve the drones is not negligible as well as \JP{handling the speed of the mothership and drones as decision variables}. These problems being very interesting are beyond the scope of the present paper and will be the focus of a follow up research line.