\documentclass[10pt,a4paper]{elsarticle}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools,amssymb}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{optidef}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{comment}
\usepackage{pgfplots}
\usepackage{soul}
\usepackage{mathrsfs}
\usepackage[ruled]{algorithm2e}
\usepackage{xspace}
\usepackage{ulem}
\usepackage{multirow}
\usepackage{bigstrut}
% \usepackage{booktabs}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\newtheorem*{remark}{Remark}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\allowdisplaybreaks

\usepackage[margin=1in]{geometry}

\def\MDR{{\sf MDRPG\xspace}}
\def\AMD{{\sf AMMDRPG\xspace}}
\def\AMDCO{{\sf AMMDRPG-CO\xspace}}
\def\AMDPO{{\sf AMMDRPG-PO\xspace}}
\def\NMD{{\sf NMDRPG\xspace}}
\def\PMD{{\sf PMDRPG\xspace}}
\definecolor{armygreen}{rgb}{0.19, 0.53, 0.43}
\definecolor{atomictangerine}{rgb}{1.0, 0.6, 0.4}
\newcommand{\JP}[1]{{\color{armygreen}#1}}
\newcommand{\CV}[1]{{\color{atomictangerine}#1}}
\newcommand{\LA}[1]{{\color{red}#1}}
\newcommand{\RE}[1]{{\color{blue}#1}}
\renewcommand{\arraystretch}{1.5}



\title{Coordinating drones with mothership vehicles: The mothership and multiple drones routing problem with Graphs}

\author[1]{Lavinia Amorosi\corref{cor1}}
\ead{lavinia.amorosi@uniroma1.it}
\author[2]{Justo Puerto\corref{cor1}}
\ead{puerto@us.es}
\author[2]{Carlos Valverde\corref{cor1}}
\ead{cvalverde@us.es}

\cortext[cor1]{Equally contributing authors}

\address[1]{Department of Statistical Sciences, Sapienza University of Rome, Italy}
\address[2]{Department of Statistical Sciences and Operational Research, University of Seville, Spain}



%\author{Lavinia Amorosi^{a}, Justo Puerto^{b}, Carlos Valverde^{b}}
%\address[1]{Department of Statistical Sciences, University of Rome, Sapienza}
%\address[2]{IMUS, Mathematical Research Institute, University of Seville}

\date{\today}

\begin{document}


\begin{abstract}
This paper considers the optimization problems that arise to coordinate a tandem between a mothership vehicle and a fleet of drones. %more than one drone. 
Each drone can be launched from the mothership to perform an operation. After completing the operations\RE{,} the drones return to the mothership to recharge \RE{the} batteries and to be ready for a new operation. Operations consist on (partially) visiting graphs with \RE{a given length} to deliver some services or to perform some surveillance/inspection activity.  The goal is to minimize the overall \RE{time of travelling made} by the mothership while satisfying some requirements in terms of percentages of visits to the target graphs. In all cases, we develop exact formulations resorting to mixed integer second\CV{-}order cone programs that are compared on a testbed of instances to assess their performance. We also develop a matheuristic algorithm that provides reasonable solutions.  Computational experiments show the usefulness of our \RE{methodology} in different scenarios. 
\end{abstract}

\begin{keyword}
Arc Routing Problems \sep Networks \sep Drones \sep Conic Programming
\end{keyword}


\maketitle


\input{introduction}
%\input{literature}
\input{description}
\input{formulations}
%\input{formulation_draft}
\input{bounds}
\input{heuristic}
% \input{Benders-like}
\input{experiments}
\input{case_study}
\input{conclusion}
\section*{Acknowledgements}
This research has been partially supported by Spanish Ministry of Education and Science/FEDER grant number  PID2020-114594GB02, and projects Junta de Andalucia P18-FR-1422, FEDER-US-1256951, CEI-3-FQM331 and  \textit{NetmeetData}: Ayudas Fundaci\'on BBVA a equipos de investigaci\'on cient\'ifica 2019.
%\section{Introduction}

% \bibliographystyle{apa}

\bibliographystyle{elsarticle-num-names}
% \printbibliography

\bibliography{bibliography2.bib}
\input{appendix}

\end{document}
